Enhancement of SDR in Thessaloniki

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 18:11

@@

@@

@@

\begin{verbatim}
2024-02-29 14:29:51.0 athan@tyler GHI_enh_04_investigate.R 1.085176 mins
\end{verbatim}

>>>>

\begin{verbatim}
Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
i Please use the `legend.position.inside` argument of `theme()` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

@@

\begin{verbatim}
Warning: The S3 guide system was deprecated in ggplot2 3.5.0.
i It has been replaced by a ggproto system that can be extended.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}

@@

\begin{verbatim}
2024-02-29 16:10:43.9 athan@tyler GHI_enh_04_investigate.R 1.399842 mins
\end{verbatim}
